---
title: "PS2_Econometrics"
author: "Isha"
date: "4/3/2022"
output:
  pdf_document: default
  html_document: default
---
```{r message=FALSE}
library(systemfit, quietly=T)
library(wooldridge, quietly=T)
library(AER, quietly=T)

data('mroz')
oursample = subset(mroz, !is.na(wage))

```
2(a)
IV Regression on Equation (i)
```{r}
eqn1 <- ivreg(hours ~ log(wage) + educ + age + kidslt6 + nwifeinc | age + kidslt6 + nwifeinc + exper + I(exper^2), data = oursample)
summary(eqn1)
```
2(a)
IV Regression on Equation (ii)
```{r}
eqn2 <- ivreg(log(wage) ~ hours + educ + exper + I(exper^2) | age + kidslt6 + nwifeinc + exper + I(exper^2), data = oursample)
summary(eqn2)
```
2(b)
After imposing exclusion restriction
```{r}
eqn1 = hours ~ log(wage) + educ + age + kidslt6 + nwifeinc
eqn2 = log(wage) ~ hours + educ + exper + I(exper^2)
eqn_system = list(eqn1, eqn2)
```


```{r}
systemfit(formula = eqn_system, inst = ~ age + kidslt6 + nwifeinc + + exper + I(exper^2), data = oursample, method = "2SLS")
```


```{r}
systemfit(formula = eqn_system, inst = ~ age + kidslt6 + nwifeinc + + exper + I(exper^2), data = oursample, method = "3SLS")
```
2(c)
Analyze the results obtained in (a) and (b) and comment on your results, in particular the significance
of the coefficients.  

For equation 1:  
2SLS and 3SLS produce different coefficients. All coefficients show impact on work hours  
- Intercepts of 2SLS are higher than intercepts of 3SLS  
- Coefficients for log(wage) in 2SLS is higher which means wage has more impact on hours in 2SLS  
- Education has negative coefficient in both 2SLS and 3SLS. The effect in 3SLS is higher.  
- Age is 2SLS has a stronger effect while it's negative. Age has positive effect in 3SLS  
- Having kids in 2SLS has a very high positive impact while that in 3SLS is negative  
- Non-wife income in both 2SLS and 3SLS have positive impact while the impact in 2SLS is higher  

For equation 2:  
Both 2SLS and 3SLS coefficients are the same however, 3SLS is more efficient.  
- The intercepts are negative  
- Hours worked has very small positive impact on log(wage)  
- Education has small positive impact on log(wage)  
- Similarly, experience has small positive impact on log(wage)  
- The square of experience has small negative impact on log(wage)  
